---
title: "Assignment"
author: "Maluhia Stark-Kinimaka "
date: "(August 21, 2023)"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
```

```{r}
  library(raster)
  library(habtools)
  library(ggplot2)
  library(dplyr)
  library(fishualize)

  plot(horseshoe)
```

### Current Lab
Geometric Ecology Lab

### Project Focus
Still developing, but along the lines of understanding how coral morphology relates to wave energy attenuation. Maybe conceptualizing how to derive coral "roughness" values by species for storm event modeling.

### Why This Course?
Quantifying how the ocean moves through and around coral reef is the coolest thing ever.

### Course Learning Goals
(1) Learn current methodologies for measuring coral geometry.
(2) Become very comfortable creating reproductions of reef structure (3D printing, SfM     model creation).
(3) Understand more deeply how geometry effects reef accretion and wave energy             attenuation using observation, R, and reproduction model analysis.
(4) Have fun.

### Experience with R
This assignment, also simultaneously taking MBIO 612 (Data Science & Fundamentals in R).

### Fun Fact
My first name is 28 letters long.
 